### 2024-06-15 out/01._Introduction/02._Moving_hallway_problem.tex
tex files

The moving sofa problem can be seen as an \emph{inverse Kakeya problem} \autocite{bae2021reverse,cabelloInverseKakeyaProblem2022}. The original Kakeya problem asks for the minimum-area chamber \(R\) in which a needle \(S\) of length 1 can be rotated the full \(360\degree\), allowing the needle to translate in its movement \autocite{kakeya1917some}. In an \emph{inverse} Kakeya problem, the shape of the chamber \(R\) is fixed and we are asked to find the shape \(S\) (the ‘needle’) of largest area that can rotate freely inside the chamber, also allowing translations in movement. For example, if the chamber is the strip \(R = \mathbb{R} \times [0, 1]\) of unit width, and the shape \(S\) has to rotate the full \(360\degree\), the problem becomes the well-studied \emph{isodiametric problem} asking for the maximum-area planar shape with diameter at most 1.

The moving sofa problem, as an inverse Kakeya problem, has the hallway as the chamber \(R = L\) and the moving sofa \(S\) as the ‘needle’ inside \(L\). The inverse Kakeya problem has been solved If the chamber \(R\) is a planar convex set; it is a consequence of the Brunn-Minkowski theorem that the largest-area shape \(S\) that can rotate the full \(360\degree\) inside a convex chamber \(R\) is the largest ball inscribed in \(R\) \autocite{cabelloInverseKakeyaProblem2022}. Since the hallway \(L\) is non-convex, however, the same approach is not effective on the moving sofa problem.

The \emph{rotation angle} \(\omega\) of a moving sofa \(S\) is defined as the clockwise angle that \(S\) rotates as it moves from \(L_H\) to \(L_V\) inside \(L\). As an inverse Kakeya problem, the angle \(\omega\) dictates how much the moving sofa \(S\) should rotate inside the hallway \(L\). Gerver’s sofa has the rotation angle \(\omega = \pi/2\). On the other hand, the unit square \([0, 1]^2\) can move inside \(L\) with only translation, so it has the rotation angle \(\omega = 0\).\footnote{As an inverse Kakeya problem, it may occur that smaller value of total rotation angle \(\omega\) will lead to less movement of \(S\) and thus a larger area of \(S\). However, the extra constraints that \(S\) has to move from horizontal side \(L_H\) to vertical side \(L_V\) penalizes the area of \(S\) as \(\omega\) gets smaller from \(\pi/2\).} Let \(\omega\) be the rotation angle of a maximum-area moving sofa. Gerver showed that we can assume \(\pi/ 3 \leq \omega \leq \pi/2\) (\autocite{gerverMovingSofaCorner1992}). Kallus and Romik improved the lower bound of \(\omega\) by showing that \(\omega \geq \arcsin(84/85) = 81.203\dots^\circ\) \autocite{kallusImprovedUpperBounds2018}. With this, we will only consider moving sofas with rotation angle \(\omega \in (0, \pi/2]\), and it seems reasonable to conjecture that a maximum-area moving sofa has \(\omega = \pi/2\).

@@

Without loss of generality, we can translate the moving sofa \(S\) horizontally and assume that \(S\) is contained in \(V_\omega\), not its arbitrary translation.\footnote{Translating the moving sofa \(S\) may invalidate the initial condition \(S \subseteq L_H\). To resolve this, we modify the \Cref{def:sofa} of a moving sofa \(S\) in so that only some \emph{translation} of \(S\) is required to be movable from \(L_H\) to \(L_V\) inside \(L\).} Then from (1), (2) and (3) above, we can always assume that \(S\) is contained in the intersection
\begin{equation}
\label{eqn:monotone}
\mathcal{M}(S) := H \cap V_\omega \cap \bigcap_{0 \leq t \leq \omega} L_t
\end{equation}
that we will define as the \emph{monotonization} of a moving sofa \(S\). The set \(\mathcal{M}(S)\) is also movable inside \(L\); observe that \(\mathcal{M}(S)\) is in each rotating hallway \(L_t\) of angle \(t \in [0, \omega]\), and see this in the perspective of the fixed hallway \(L\) instead of the moving hallway \(L_t\) and vary \(t\) from \(0\) to \(\omega\). So the monotonization \(\mathcal{M}(S)\) is a moving sofa containing \(S\)\footnote{This uses an implicit assumption that the intersection \(\mathcal{M}(S)\) should be connected. Indeed, \autocite{gerverMovingSofaCorner1992} assumes the connectedness of \(\mathcal{M}(S)\) in its proof of Theorem 1 of \autocite{gerverMovingSofaCorner1992} without any justification. We justify this assumption rigorously in \Cref{thm:monotonization-is-connected}.} (\Cref{thm:monotonization-is-sofa}), and we call such a sofa \(\mathcal{M}(S)\) from monotonization a \emph{monotone sofa} (\Cref{def:monotone-sofa}). Since any moving sofa \(S\) is contained in a larger monotone sofa \(\mathcal{M}(S)\), we only need to consider monotone sofas for the moving sofa problem.

>>>>

The \emph{rotation angle} \(\omega\) of a moving sofa \(S\) is defined as the clockwise angle that \(S\) rotates as it moves from \(L_H\) to \(L_V\) inside \(L\). Gerver’s sofa has the rotation angle \(\omega = \pi/2\). On the other hand, the unit square \([0, 1]^2\) can move inside \(L\) with only translation, so it has the rotation angle \(\omega = 0\). Let \(\omega\) be the rotation angle of a maximum-area moving sofa. Gerver proved that we can assume \(\pi/ 3 \leq \omega \leq \pi/2\) \autocite{gerverMovingSofaCorner1992}. Kallus and Romik improved the lower bound of \(\omega\) by showing that \(\omega \geq \arcsin(84/85) = 81.203\dots^\circ\) \autocite{kallusImprovedUpperBounds2018}. With this, we will only consider moving sofas with rotation angle \(\omega \in (0, \pi/2]\), and it seems reasonable to conjecture that a maximum-area moving sofa has \(\omega = \pi/2\).

@@

Without loss of generality, we can translate the moving sofa \(S\) horizontally and assume that \(S\) is contained in \(V_\omega\), not its arbitrary translation.\footnote{Translating the moving sofa \(S\) may invalidate the initial condition \(S \subseteq L_H\). To resolve this, we relax the \Cref{def:sofa} of a moving sofa \(S\) in so that only some translation of \(S\) is required to be movable from \(L_H\) to \(L_V\) inside \(L\).} Then from (1), (2) and (3) above, we can always assume that \(S\) is contained in the intersection
\begin{equation}
\label{eqn:monotone}
\mathcal{M}(S) := H \cap V_\omega \cap \bigcap_{0 \leq t \leq \omega} L_t
\end{equation}
that we will define as the \emph{monotonization} of a moving sofa \(S\). The set \(\mathcal{M}(S)\) is also movable inside \(L\); observe that \(\mathcal{M}(S)\) is in each rotating hallway \(L_t\) of angle \(t \in [0, \omega]\), and see this in the perspective of the fixed hallway \(L\) instead of the moving hallway \(L_t\) and vary \(t\) from \(0\) to \(\omega\). So the monotonization \(\mathcal{M}(S)\) is a moving sofa containing \(S\) (\Cref{thm:monotonization-is-sofa})\footnote{This uses an implicit assumption that the intersection \(\mathcal{M}(S)\) should be connected. Indeed, \autocite{gerverMovingSofaCorner1992} assumes the connectedness of \(\mathcal{M}(S)\) in its proof of Theorem 1 of \autocite{gerverMovingSofaCorner1992} without further justification. We prove this assumption rigorously in \Cref{thm:monotonization-is-connected}.}, and we call such a sofa \(\mathcal{M}(S)\) from monotonization a \emph{monotone sofa} (\Cref{def:monotone-sofa}). Since any moving sofa \(S\) is contained in a larger monotone sofa \(\mathcal{M}(S)\), we only need to consider monotone sofas for the moving sofa problem.

### 2024-06-15 out/25._Conditional_upper_bound_A1/00._Preface.tex
tex files

We prove the generalized \Cref{thm:main-cap} of the main \Cref{thm:main} in this section. We do this by constructing and maximizing the upper bound \(\mathcal{A}_1\) of the sofa area functional \(\mathcal{A}\) as described in the introduction.

>>>>

In this \Cref{sec:conditional-upper-bound-a1}, we prove the generalized \Cref{thm:main-cap} of the main \Cref{thm:main} by establishing a conditional upper bound \(\mathcal{A}_1 : \mathcal{K}_\omega \to \mathbb{R}\) of the sofa area functional \(\mathcal{A} : \mathcal{K}_\omega \to \mathbb{R}\). For any monotone sofa \(S\) satisfying the injectivity condition, we prove \(\mathcal{A}_1(K) \geq \mathcal{A}(K)\). Then we calculate the maximum value \(1 + \omega^2/2\) of \(\mathcal{A}_1\).

### 2024-06-15 out/A1._Convex_bodies.tex
tex files

\input{out/A1. Convex bodies/00. Preface.tex}
\subsection{Vertex and support function}
\label{sec:vertex-and-support-function}
\input{out/A1. Convex bodies/05. Vertex and support function.tex}

\subsection{Lebesgue-Stieltjes measure}
\label{sec:lebesgue-stieltjes-measure}
\input{out/A1. Convex bodies/07. Lebesgue-Stieltjes measure.tex}

\subsection{Surface area measure}
\label{sec:surface-area-measure}
\input{out/A1. Convex bodies/10. Surface area measure.tex}

\subsection{Parametrization of boundary}
\label{sec:parametrization-of-boundary}
\input{out/A1. Convex bodies/15. Parametrization of boundary.tex}

\subsection{Normal angles}
\label{sec:normal-angles}
\input{out/A1. Convex bodies/20. Normal angles.tex}

\subsection{Mamikon's theorem}
\label{sec:mamikon's-theorem}
\input{out/A1. Convex bodies/25. Mamikon's theorem.tex}

>>>>

\input{out/A1._Convex_bodies/00._Preface.tex}
\subsection{Vertex and support function}
\label{sec:vertex-and-support-function}
\input{out/A1._Convex_bodies/05._Vertex_and_support_function.tex}

\subsection{Lebesgue-Stieltjes measure}
\label{sec:lebesgue-stieltjes-measure}
\input{out/A1._Convex_bodies/07._Lebesgue-Stieltjes_measure.tex}

\subsection{Surface area measure}
\label{sec:surface-area-measure}
\input{out/A1._Convex_bodies/10._Surface_area_measure.tex}

\subsection{Parametrization of boundary}
\label{sec:parametrization-of-boundary}
\input{out/A1._Convex_bodies/15._Parametrization_of_boundary.tex}

\subsection{Normal angles}
\label{sec:normal-angles}
\input{out/A1._Convex_bodies/20._Normal_angles.tex}

\subsection{Mamikon's theorem}
\label{sec:mamikon's-theorem}
\input{out/A1._Convex_bodies/25._Mamikons_theorem.tex}
